%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	{ \fontsize{12}{14.4} \textcolor{black}{\textbf{\MakeUppercase{Brian Thompson}}}} % First name
	\vspace{6pt}
	{\Large Lead Software Engineer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    % The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
    \icon{Phone}{11}{(636)426-0447}\\
    \icon{MapMarker}{11}{St. Louis, MO}\\	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    \icon{Envelope}{11}{\href{mailto:brianrobt@pm.me}{brianrobt@pm.me}}\\	
    \icon{Github}{11}{\href{https://github.com/brianrobt}{github.com/brianrobt}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/brian-r-thompson}{/in/brian-r-thompson}}\\    
\end{minipage}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
    \vspace{-6pt} 
\par  First and foremost, I value hard work, honesty, and grit. I love being in a team where I can contribute my expertise
while simultaneously learning new things and growing my skillset. While I’m not honing my craft, I’m either with my
wife and children, walking our dog, at the gym, or reading about history and philosophy.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Python, Java, Groovy, Ruby, JavaScript, TypeScript, Bash, SQL  
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      AWS, Azure, Docker, Terraform, Jenkins, SaltStack, Gradle, Maven, Chef, Linux, Git, Tomcat, Apache, JBoss
    \end{minipage} 
\end{minipage}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{2008-2014}
		{Truman State University}
		{}
		{B.S. Computer Science}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
	        {6/2022 -- 2/2024}
		{Lead Site Reliability Engineer}
		{Mastercard}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Configuration, maintenance, management, deployment, and high-availability uptime of over 100 Thales
		  Luna HSMs, and 50+ supporting virtual machines.
            \item Lead the design and implementation of the company-wide Luna HSM AWS Hybrid Cloud initiative.
	    \item Mentored and supported junior team members every day.
	    \item Developed and designed automation solutions, including writing Python packages, Jenkins pipelines, shell
		  scripts, Chef cookbooks, and other custom tools from scratch.
	    \item Wrote and maintained detailed technical documentation, including operational procedures, designs, and
		  infrastructure lists.
	    \item Managed and improved change processes for Luna HSMs and supporting infrastructure.
	    \item Managed stakeholders interests while keeping the operational interests at heart.
	    \item Developed Luna HSM operational design for a hybrid environment (on-prem HSMs and clients in AWS/Azure).
	    \item Lead the migration of Azure VMs from CentOS 7 to RHEL 8 for my team.
	    \item Collaborated with dozens of different stakeholders and individuals from other teams across the company
		  on a daily basis.
	    \item Increased procedural speed without sacrificing quality.
	    \item Provided a solid, reliable, and streamlined customer experience.
	    \item Improved production deployment and operational efficiencies for a widely used shared micro service.
	    \item Wrote audit reports, and addressed gaps to meet audit requirements.
	    \item Lead cloud operations for a widely used cryptography microservice.
	    \item Performed application deployments and infrastructure management in Azure with Terraform.
	\end{itemize}}
	\entry
		{10/2021 -- 4/2022}
		{Cloud Data Engineer}
		{Ameren}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Configured and automated AWS infrastructure using Terraform (including AWS RedShift, IAM, SSO,
		  CloudFront, Lambda, S3, and RDS).
            \item Developed and delivered multiple Databricks pipelines that transformed raw data into usable, formatted
		  data that could then be used by the Data Scientists.
	    \item Designed and implemented an AD-based security strategy so that the Data Scientists could use Databricks
		  in a controlled manner.
	\end{itemize}}
	\entry
		{11/2018 -- 10/2021}
		{Senior DevOps Engineer}
		{Mastercard}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Specialized in Application Release Automation (ARA).
            \item Maintained custom SaltStack modules for deploying applications to various middleware components (e.g.,
		  Apache, Tomcat, JBoss, WebSphere).
	    \item Wrote extensive unit and integration tests.
	    \item Worked with development teams to create and prioritize new features.
	    \item Maintained supporting infrastructure with Chef Cookbooks.
	    \item Built a new ARA framework from scratch with Chef Habitat.
	    \item Migrated the existing ARA SaltStack solution to the new Chef Habitat framework.
	    \item Wrote and maintained Jenkins pipelines, shared libraries, and job templates.
	    \item Used Splunk to monitor infrastructure health and gather usage metrics of the various ARA modules.
	\end{itemize}}
	\entry
		{3/2017 -- 11/2018}
		{Software Engineer}
		{Mastercard}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Built an application for bank customers that netted \$400m USD in the first year after release.
            \item Worked on a suite of web applications that were directly used by customers in production.
	    \item Wrote a UI in Angular (from Alpha release to 6.0).
	    \item Collaborated on feature development and design.
	    \item Wrote a transacations-based web service in Java.
	    \item Spun up a Jenkins server for team’s immediate use before Jenkins was widespread across the corporation.
	    \item Dedicated an RHEL VM internally exposed to the company since multiple teams demanded its usage.
	    \item Managed LDAP roles and permissions.
	    \item Created a Git branching strategy that the team still uses today.
	\end{itemize}}
	\entry
		{7/2015 -- 3/2017}
		{Associate Software Engineer}
		{Mastercard}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Ported an internal Java CLI tool to an AngularJS web app and a RESTful Java API.
            \item Designed a GUI from wireframes to implementation.
	    \item Used many AngularJS (1.x) modules to manage common tasks like routing, web services, and animations.
	\end{itemize}}
	\entry
		{6/2012 -- 3/2015}
		{Junior Software Engineer (Intern)}
		{Tapestry Solutions}
		{\vspace{-10pt}
\par I was an intern at Tapestry Solutions in 2012, which changed to a part-time role while I was finishing up
school. I stayed at the company until a few months after I graduated.
\break
\par While I was there, I worked with Hudson/Jenkins, Kettle (an ETL tool), AWS (EC2 and S3), Java, Bash,
and Linux. My role was heavy with automating tasks that the more experienced team needed. The company
had a requirement that you had to have at least 10 years of experience and be high-performing. I was the first
intern there. It was a great learning experience working with engineers that were so much more experienced than
myself, and helped jump-start my career significantly.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{26mm} \textbf{English} - Native, \textbf{Spanish} - Intermediate

%----------------------------------------------------------------------------------------

\end{document}
